Death By Dropdown?

### 2025-04-01 conference-materials/2025_shiny-conf/slides.qmd
Introduce BID framework and implement via SoundPulse case study
- Added BID framework explanation
- Incorporated SoundPulse as a composite case study to contextualize dashboard design issues
- Implemented principles using `{reactable}` and `{echarts4r}` code examples
- Demonstrated key cognitive and behavioral design concepts
- Included interactive UI elements like toggle switches, comments, and progressive disclosure to enhance decision-making
- Concluded with `{bidux}` introduction and outcomes showing tangible improvements

::: {.column width="40%"}
![](https://media.giphy.com/media/v1.Y2lkPTc5MGI3NjExMzhmY2YwMDA5MWFjOTlmN2Y0MGE2YjQzNmI5YTEzZDE3MWE1ZDIwNSZlcD12MV9pbnRlcm5hbF9naWZ5X2dpZiZjdD1n/32mC2kXYWCsg0/giphy.gif)
:::
::::

@@

::: {.fragment}

::: {.r-fit-text}
We can guide users effortlessly to insights
:::
:::

@@

::: {.nonincremental}
1. **Notice** the Problem
2. **Interpret** the User's Need
3. **Structure** the Dashboard
4. **Anticipate** User Behavior
5. **Validate** & Empower the User
:::

> _(placeholder for BID framework visual)_

::: {.notes}
- This framework distills psychological principles into actionable steps
- Each stage builds on the previous one
- The framework is grounded in behavioral science, communication theory, and UX design
:::

@@

## Real-World Patterns, Not Just Theory {.center background-color="#FFFFFF"}

::: {.columns}
::: {.column width="50%"}
### Before BID:
- Information overload
- No clear story
- Cognitive friction
- Unused features
- Unclear next steps
:::

::: {.column width="50%"}
### After BID:
- Focused on key user needs
- Clear narrative structure
- Reduced cognitive load
- Bias-aware design
- Actionable insights
:::
::::

::: {.fragment}
### The outcome:
Users make faster, better decisions with less cognitive effort
:::

::: {.r-fit-text}
**Screenshots**: Before & After applying BID framework across stages
:::

> _(placeholder for visual comparison of UI examples)_

## Implementation Demo {.center background-color="#F9F9F9"}

::: {.r-fit-text}
Hands-on example using `{reactable}` + `{echarts4r}` to implement Stages 1–5
:::

> _(placeholder for staged code walkthrough or animated screen recording)_

## From Framework to Workflow {.center background-color="#E6F0FF"}

::: {.r-fit-text}
Meet `{bidux}`: Your BID Assistant for Shiny
:::

- 🧠 Five structured helpers: `bid_notice()` to `bid_validate()`
- 📚 Concept browser: `bid_concept("processing_fluency")`
- 📄 Built-in documentation + report generation
- 🔌 Works with `{rhino}` and your existing apps

> _(placeholder screenshot: console usage or UI screen of `{bidux}` helpers)_

## What bidux Looks Like {.background-color="#F9F9F9"}

@@

@@

::: {.nonincremental}
1. **BID** helps reduce friction and improve decisions
2. **Reactable + echarts4r** bring BID to life
3. **`bidux`** supports you in applying BID at every stage
4. Build dashboards that guide — not overwhelm — your users
:::

@@

>>>>

::: {.column width="40%"}
![](https://media0.giphy.com/media/v1.Y2lkPTc5MGI3NjExbzVhM3d3MjJvYTNyc3puM2E0cmduZjFweXhrczNwcXI0b3FhN203aCZlcD12MV9pbnRlcm5hbF9naWZfYnlfaWQmY3Q9Zw/l44Q5OXJ6qaNr838Q/giphy.gif)
:::
::::

::: {.notes}
**Opening Hook**: Begin with energy! Make eye contact across the room.

- Start by acknowledging the shared pain point everyone recognizes
- Emphasize the emotional response users have when facing cluttered dashboards
- Mention that this is costing organizations real money through delayed decisions
- "Dashboard rot" = dashboards that get built but never used
- Ask for a show of hands: "How many of you have abandoned using a dashboard because it was too complex?" (engage audience early)
:::

@@

:::: {.columns .fragment}
::: {.column width="60%"}
<br>

SoundPulse's market research team was drowning in data, unable to extract meaningful insights from their complex dashboards.
:::

::: {.column width="40%"}
<br>

![](https://media2.giphy.com/media/v1.Y2lkPTc5MGI3NjExeXFwNHV6N3B4cmIzaTY3ajYwYTRkNG95ZWtxdjB5cTE1djRibGRydCZlcD12MV9pbnRlcm5hbF9naWZfYnlfaWQmY3Q9Zw/xT0BKiK5sOCVdBUhiM/giphy.gif){width="90%"}
:::
::::

::: {.notes}
**Transition to Solution**: Shift to a hopeful, inspiring tone here.

- The central thesis of our talk: storytelling vs. data dumping
- Introduce SoundPulse as our case study - they're a composite client...competitor of Spotify
- Their market research team needed to present competitor analysis to executives
- Emphasize that this shift is both attitudinal and technical
- Preview: "We'll show you exactly how this transformation works using real code examples"
- When the GIF appears, pause briefly - people will laugh at the "drowning in paper" visual
:::

::: {.r-fit-text}
**SoundPulse Market Research Dashboard Transformation**
:::

:::: {.columns}
::: {.column width="50%"}
### Before BID:
<!-- Dashboard with overwhelming filters and complex tables -->
![](img/before_bid_dashboard.png){width="95%"}

- 14 dropdown filters
- 8 tabs of dense data tables
- No clear hierarchy of information
:::

::: {.column width="50%"}
### After BID:
<!-- Streamlined dashboard with clear information hierarchy -->
![](img/after_bid_dashboard.png){width="95%"}

- Guided narrative pathway
- Focused insights by segment
- Progressive disclosure of details
:::
::::

::: {.notes}
**Show Impact**: Use before/after contrast to demonstrate value.

- Walk through the key issues with the "before" dashboard:
  * "Look at all those filters - users had to make decisions before seeing ANY data"
  * "No guidance on where to start - cognitive overload from the beginning"
- Highlight transformative elements in the "after" version:
  * "Notice how there's a clear path through the data"
  * "Progressive disclosure - you see what you need first, then can dig deeper"
  * "The interface itself tells a story about what matters most"
- Mention that this resulted in 43% faster decision-making (preview of results)
:::

@@

:::: {.columns}
::: {.column width="60%"}
1. **Notice** the Problem
2. **Interpret** the User's Need
3. **Structure** the Dashboard
4. **Anticipate** User Behavior
5. **Validate** & Empower the User
:::

::: {.column width="40%"}
![The BID Framework](img/The_BID_framework.png)
::: 
::::

::: {.notes}
**Framework Introduction**: Slow down here - this is the core methodology.

- The 5 stages form an acronym: NISAV (pronounced "knee-sav")
- Each stage builds on psychological principles but translates to practical actions
- Emphasize this isn't just theory - it's a practical workflow for developers
- Preview: "We'll walk through each stage with SoundPulse's case study"
- Mention these are iterative, not strictly linear - you can revisit earlier stages
- Personal anecdote: "We developed this framework after seeing the same patterns of dashboard failure across industries"
:::

@@

::: {.notes}
**Context Setting**: Position the framework within the broader field.

- Acknowledge that this builds on existing work - "We're standing on the shoulders of giants"
- Emphasize the unique integration of disciplines - behavioral economics + UX + data viz
- Key difference from other approaches: process-oriented vs. checklist approach
- "What makes BID different is that it's specifically designed for analytics dashboards"
- This is important context before diving into the stages in detail
- Quickly mention some influences: "Edward Tufte's data visualization principles, Nielsen's heuristics, and Kahneman's work on cognitive biases"
:::

## Case Study: Stages 1-3 {background-color="#F9F9F9"}

:::: {.columns}
::: {.column width="50%"}
### SoundPulse's Challenges:

- **Stage 1: Notice**
    - Complex filtering overwhelmed users
    - 72% reported feeling confused
- **Stage 2: Interpret**
    - Users couldn't quickly process information
    - Key insights buried in text and numbers
- **Stage 3: Structure**
    - Related elements scattered throughout UI
    - No prioritization of important metrics
:::

::: {.column width="50%"}
### BID Principles Applied:

- **Stage 1: Notice**
    - Cognitive Load Theory
    - Hick's Law
- **Stage 2: Interpret**
    - Processing Fluency
    - Data Storytelling Framework
- **Stage 3: Structure**
    - Principle of Proximity
    - Default Effect
    - Dual-Processing Theory
:::
::::

::: {.notes}
**Case Study Setup**: Establish context for upcoming code examples.

- "Let's see how SoundPulse applied the first three stages of the BID framework"
- For Stage 1 (Notice): "They identified how filtering complexity was causing cognitive overload"
- For Stage 2 (Interpret): "They discovered users needed to process key metrics instantly"
- For Stage 3 (Structure): "They needed to group related elements and establish clear visual hierarchy"
- "Now let's look at how they implemented these principles using {reactable}"
- Transition: "We'll start with a basic implementation and build up to more advanced features"
:::

## Implementation Demo: {reactable} Basics {background-color="#F9F9F9"}

::: {.r-fit-text}
Using `{reactable}` to implement Stages 1-3
:::

```r
reactable(
  soundpulse_data,
  # Stage 1: Cognitive Load Theory - Grouped structure reduces complexity
  groupBy = "Claim",

  # Stage 2: Processing Fluency - Color coding for instant insights
  columns = list(
    Metric1 = colDef(
      style = function(value) {
        # Color coding enhances processing fluency
        if (value > 50) {
          list(background = "rgba(0, 128, 128, 0.2)", 
               color = "#006666", fontWeight = "bold")
        } else if (value < 30) {
          list(background = "rgba(255, 140, 0, 0.2)", 
               color = "#DD8500", fontWeight = "bold")
        }
      }
    )
  )
)
```

::: {.notes}
**Basic Implementation**: Start with the foundational elements.

- "Let's break down the simplest implementation of BID principles in reactable"
- **WOW MOMENT #1**: "The groupBy parameter does double duty here - it addresses cognitive load from Stage 1 while creating visual hierarchy for Stage 3"
- "Color coding isn't just for aesthetics - it directly implements processing fluency from Stage 2"
- "Notice how the conditional styling creates instant visual cues for good and concerning metrics"
- "This simple implementation already reduces cognitive load and enhances processing - but we can do more"
- Transition: "Now let's add more advanced features to handle Stage 3 principles..."
:::

## Implementation Demo: {reactable} Advanced {background-color="#F9F9F9"}

::: {.r-fit-text}
Enhanced Implementation with Bar Charts, Grouping, and Progressive Disclosure
:::

```r
reactable(
  soundpulse_data,
  # Stage 3: Principle of Proximity - Group related elements visually
  columnGroups = list(
    colGroup(name = "System 1 - Quick Insights", 
             columns = c("Metric1", "Metric2")),
    colGroup(name = "System 2 - Detailed Analysis", 
             columns = c("Metric3", "Metric4"))
  ),

  # Stage 2 & 3: Enhanced Processing Fluency with bar charts
  columns = list(
    Metric1 = colDef(
      cell = function(value) create_bar_chart_cell(value, "metric1"),
      html = TRUE
    )
  ),

  # Progressive disclosure supports Cognitive Load Theory
  details = function(index) {
    # Only show details when requested
    detailed_data <- segment_details[segment_details$claim_id == 
                                     soundpulse_data$Claim[index], ]
    div(
      style = "padding: 1rem",
      reactable(detailed_data, outlined = TRUE, striped = TRUE)
    )
  }
)
```

::: {.notes}
**Advanced Features**: Highlight sophisticated techniques.

- "Now we're implementing more advanced BID principles with reactable"
- **WOW MOMENT #2**: "The columnGroups feature implements Dual-Processing Theory by separating quick insights (System 1) from detailed analysis (System 2)"
- "The create_bar_chart_cell function creates custom HTML for enhanced bar charts with tooltips"
- **WOW MOMENT #3**: "Progressive disclosure with the details parameter is one of the most powerful cognitive load reduction techniques - users only see the details when they need them"
- "This nested reactable implementation lets users drill down into detailed data without being overwhelmed"
- "All of these features work together to create a dashboard that respects how humans actually process information"
- Ask audience: "How many of you have used columnGroups or details in reactable?" (interactive moment)
- Transition: "Now let's see how these principles look in the final implementation..."
:::

## {reactable} Implementation: Visual Result {background-color="#F9F9F9"}

::: {.r-stack}
![](img/reactable_example_1.png){width="75%"}
![](img/reactable_example_2.png){.fragment width="75%"}
![](img/reactable_example_3.png){.fragment width="75%"}
![](img/reactable_example_4.png){.fragment width="75%"}
:::

::: {.notes}
**Visual Impact**: Connect code to visual results.

- "Here's what our reactable implementation looks like in practice"
- For each image as it appears:
  * First image: "Notice how the grouped bars implement Stage 1 principles by reducing cognitive load"
  * Second image: "The dynamic legend addresses Hick's Law by simplifying choices"
  * Third image: "Color coding enhances processing fluency from Stage 2"
  * Fourth image: "The grouping clearly implements the Principle of Proximity from Stage 3"
- "Each of these visual elements directly ties to a principle from the BID framework"
- "This is the power of intentional design - every element has a psychological purpose"
- Transition: "Now let's look at our final reactable example with team collaboration features..."
:::

## {reactable} Implementation: Team Collaboration {background-color="#F9F9F9"}

```r
# Comments and annotation feature for Stage 5: Validate & Empower
columns = list(
  # Other columns as before
  comments = colDef(
    name = "Comments",
    cell = function(value, index) {
      comment_id <- paste0("comment-", index)
      tags$div(
        class = "comment-container",
        tags$textarea(
          id = comment_id,
          class = "form-control comment-box",
          rows = "2",
          placeholder = "Add a comment...",
          value = value,
          onchange = sprintf("saveComment(%s, this.value)", index)
        ),
        tags$div(
          class = "comment-buttons mt-1",
          tags$button(
            type = "button", 
            class = "btn btn-sm btn-outline-primary me-1",
            onclick = sprintf("addHighlight(%s)", index),
            "Highlight"
          ),
          tags$button(
            type = "button",
            class = "btn btn-sm btn-outline-secondary",
            onclick = sprintf("clearComment(%s)", index),
            "Clear"
          )
        )
      )
    },
    html = TRUE,
    width = 250
  )
)
```

::: {.notes}
**Collaboration Features**: Connect to later BID stages.

- "This example actually implements principles from Stage 5: Validate & Empower through collaboration"
- **WOW MOMENT #4**: "The comment and highlight functionality allows team members to collaborate directly within the dashboard"
- "This addresses the Cooperation & Coordination principle from Stage 5"
- "Notice how we're using custom HTML within reactable cells to create a mini application"
- "The onchange and onclick handlers connect to JavaScript functions for saving comments and highlighting rows"
- "This transforms the dashboard from a static display to a collaborative decision-making tool"
- "Similar features in tools like Google Sheets have transformed how teams work - we can bring that same power to Shiny"
- Transition: "Now that we've seen how to implement Stages 1-3 with reactable, let's move to Stages 4-5..."
:::

## Case Study: Stages 4-5 {background-color="#F9F9F9"}

:::: {.columns}
::: {.column width="50%"}
### SoundPulse's Challenges:

- **Stage 4: Anticipate**
    - Executives comparing metrics without context
    - Teams interpreting data through confirmation bias
    - Different perspectives needed for different teams
- **Stage 5: Validate**
    - Insights lost after dashboard sessions
    - No clear path to consensus
    - Teams needed actionable summaries
:::

::: {.column width="50%"}
### BID Principles Applied:

- **Stage 4: Anticipate**
    - Anchoring Effect
    - Framing & Loss Aversion
    - Confirmation Bias
- **Stage 5: Validate**
    - Peak-End Rule
    - Cooperation & Coordination
    - Beautiful-Is-Good Stereotype
:::
::::

::: {.notes}
**Advanced Stages**: Set up context for echarts4r examples.

- "Now we'll look at how SoundPulse tackled the later stages of the BID framework"
- For Stage 4 (Anticipate): "They needed to address how cognitive biases were affecting interpretation"
- For Stage 5 (Validate): "They needed to create lasting impressions and facilitate team consensus"
- "These stages address the subtler psychological aspects of data interpretation"
- "Now let's see how they implemented these principles using {echarts4r}"
- "We'll start with basic chart implementation and build up to more interactive features"
:::

## Implementation Demo: {echarts4r} Basics {background-color="#F9F9F9"}

::: {.r-fit-text}
Using `{echarts4r}` to implement Stages 4-5
:::

```r
# Create a static gauge chart
create_static_gauge <- function(value, column_name, tooltip_text = NULL) {
  chart <- e_charts() |>
    e_gauge(
      value,
      startAngle = 180,
      endAngle = 0,
      detail = list(formatter = "{value}%", fontSize = 14),
      pointer = list(show = FALSE),
      axisLine = list(
        lineStyle = list(
          color = list(
            c(round(value / 100, 2), "#1c6d7d"),
            c(1, "#d2d2d2")
          ),
          width = 50
        )
      )
    ) |>
    e_title(column_name)

  if (!is.null(tooltip_text)) {
    chart <- chart |> e_tooltip(
      formatter = htmlwidgets::JS(
        sprintf("function(params) { return '%s'; }", tooltip_text)
      )
    )
  }

  return(chart)
}
```

::: {.notes}
**Gauge Charts**: Start with visually impactful elements.

- "Let's start with gauge charts that implement processing fluency principles from Stage 2"
- **WOW MOMENT #5**: "The e_gauge function creates visually intuitive displays that are instantly comprehensible"
- "Notice how we're customizing the gauge to eliminate unnecessary elements like the pointer"
- "The color gradient visually reinforces the value - showing progress as filled area"
- "Custom tooltips provide additional context to mitigate confirmation bias from Stage 4"
- "This function encapsulates a reusable pattern that we can apply consistently across metrics"
- "The visual simplicity of gauges reduces cognitive load while maintaining information richness"
- Transition: "Now let's add reference benchmarks to address the Anchoring Effect..."
:::

## Implementation Demo: {echarts4r} Reference Lines {background-color="#F9F9F9"}

::: {.r-fit-text}
Adding Benchmark References to Address Anchoring Effect
:::

```r
# Create a static bar chart with benchmark
create_static_bar <- function(
  value, column_name, benchmark = NULL, 
  tooltip_text = NULL, frame_type = "progress") {
  # Chart creation code...

  # Add benchmark line if provided
  if (!is.null(benchmark)) {
    chart <- chart |>
      e_mark_line(
        data = list(xAxis = benchmark, name = "Benchmark"),
        symbol = "none",
        lineStyle = list(color = "#ff9000", width = 2, type = "dashed"),
        label = list(show = TRUE, formatter = "{b}: {c}%")
      )
  }

  return(chart)
}

# Usage in layout
layout_columns(
  col_widths = c(4, 4, 4),
  div(create_static_bar(65, "KPI 1", 50, "Benchmark is industry average")),
  div(create_static_bar(45, "KPI 2", 50, "Benchmark is industry average")),
  div(create_static_bar(72, "KPI 3", 50, "Benchmark is industry average"))
)
```

::: {.notes}
**Reference Lines**: Highlight the Anchoring Effect implementation.

- "This code directly implements the Anchoring Effect principle from Stage 4"
- **WOW MOMENT #6**: "The e_mark_line feature provides visual reference points that anchor interpretation"
- "Without these reference lines, values like 65% or 45% have no context - are they good or bad?"
- "By providing benchmarks, we're giving users appropriate anchors for comparison"
- "Notice the styling choices - orange dashed line creates visual distinction from the data"
- "The tooltip provides additional context about the benchmark source"
- "This simple addition dramatically improves how users interpret the data"
- Transition: "Now let's look at our most sophisticated implementation - the framing toggle..."
:::

## Implementation Demo: {echarts4r} Framing Toggle {background-color="#F9F9F9"}

::: {.r-fit-text}
Implementing Framing & Loss Aversion Principles with Interactive Toggle
:::

```r
# Frame toggle UI
frame_toggle <- div(
  class = "frame-toggle-container",
  span(class = "frame-toggle-label", "Framing:"),
  div(
    class = "btn-group",
    role = "group",
    `aria-label` = "Framing toggle",
    tags$button(
      id = "progress-btn",
      class = "btn btn-sm btn-primary active",
      type = "button",
      "Progress"
    ),
    tags$button(
      id = "gap-btn",
      class = "btn btn-sm btn-outline-primary",
      type = "button",
      "Gap"
    )
  )
)

# JavaScript for toggling
tags$script(HTML("
  function toggleFraming(framingType) {
    if (framingType === 'progress') {
      // Show progress charts, hide gap charts
      document.querySelectorAll('.framing-chart:nth-child(1)').forEach(function(chart) {
        chart.classList.remove('hidden-chart');
      });
      document.querySelectorAll('.framing-chart:nth-child(2)').forEach(function(chart) {
        chart.classList.add('hidden-chart');
      });
    } else {
      // Show gap charts, hide progress charts
      document.querySelectorAll('.framing-chart:nth-child(1)').forEach(function(chart) {
        chart.classList.add('hidden-chart');
      });
      document.querySelectorAll('.framing-chart:nth-child(2)').forEach(function(chart) {
        chart.classList.remove('hidden-chart');
      });
    }
  }
"))
```

::: {.notes}
**Framing Toggle**: Demonstrate psychological impact of framing.

- "This is our most powerful implementation of a BID principle - the Framing Toggle"
- **WOW MOMENT #7**: "We're creating two different views of the same data to demonstrate how framing affects perception"
- "The 'Progress' frame emphasizes achievement - how far we've come"
- "The 'Gap' frame emphasizes what remains - how far we still need to go"
- "This directly implements the Framing & Loss Aversion principle from Stage 4"
- "The JavaScript allows users to switch between frames without a full page reload"
- "Different teams at SoundPulse used different frames - marketing used Progress, product used Gap"
- "This is a powerful example of how design choices influence decision-making"
- Interactive moment: "Let me show you how this works in practice..." (if possible, demonstrate live)
- Transition: "Now let's see how these elements come together in the complete dashboard..."
:::

## {echarts4r} Implementation: Visual Result {background-color="#F9F9F9"}

::: {.r-fit-text}
Complete Dashboard with Multiple BID Principles
:::

::: {.r-stack}
![](img/echarts_example_1.png){width="75%"}
![](img/echarts_example_2.png){.fragment width="75%"}
![](img/echarts_example_3.png){.fragment width="75%"}
:::

::: {.notes}
**Complete Dashboard**: Show the integrated result.

- "Here's the complete dashboard implementing multiple BID principles with echarts4r"
- For each image as it appears:
  * First image: "The gauge charts provide instant comprehension while reference lines provide anchoring"
  * Second image: "The framing toggle allows different perspectives on the same data"
  * Third image: "The summary cards implement the Peak-End Rule from Stage 5"
- "Notice how the consistent visual design implements the Beautiful-Is-Good Stereotype from Stage 5"
- "The card-based layout creates clear visual hierarchy and reduces cognitive load"
- "Every element in this dashboard has a specific psychological purpose"
- "This is what we mean by behavior-informed design - intentional choices based on how humans think"
- Transition: "Now let's look at how framing affects decision-making in more detail..."
:::

## Interactive Demonstration: Framing Effect {background-color="#E6F0FF"}

### How Framing Affects Perception & Decision-Making

:::: {.columns .nonincremental}
::: {.column width="50%"}
#### Progress Framing:
![](img/progress_framing.png){width="90%"}
:::

::: {.column width="50%"}
#### Gap Framing:
![](img/gap_framing.png){width="90%"}
:::
::::

::: {.fragment}
**SoundPulse Results:** Marketing team preferred progress framing for stakeholder presentations, while product teams found gap framing more actionable for development priorities.
:::

::: {.notes}
**Framing Effect**: Emphasize psychological impact.

- "This slide demonstrates the power of framing in action - same exact data, completely different psychological impact"
- "Progress framing creates motivation and highlights achievement - 'We're 65% there!'"
- "Gap framing creates urgency and focuses on what remains to be done - '35% still to go!'"
- "This psychological principle has been demonstrated in countless studies"
- "Present a 90% survival rate vs. a 10% mortality rate - people react completely differently"
- When the results fragment appears: "At SoundPulse, this had real organizational impact"
- "Marketing needed to show progress to build confidence with stakeholders"
- "Product teams needed to focus on gaps to prioritize development resources"
- "The toggle feature meant both teams could use the same dashboard for different purposes"
- "This is why understanding psychological principles is so powerful for dashboard design"
- Interactive moment: "Think about your own dashboards - are you framing data in a way that drives the right decisions?"
- Transition: "Now let's talk about how we're making these principles accessible to every developer..."
:::

## From Framework to Workflow: Introducing {bidux} {.center background-color="#E6F0FF"}

:::: {.columns}
::: {.column width="60%"}
`{bidux}` is our new R package currently in **Phase 1 development** that helps implement the BID framework:

- **Current Features:**
  - 📚 Concept browser: `bid_concept("processing_fluency")`
  - 🧠 Documentation functions: `bid_notice()` to `bid_validate()`

- **Coming Soon (Phase 2-4):**
  - 🛠️ UI Component Library
  - 🤖 LLM Integration 
  - 📊 Testing and Validation Tools
:::

::: {.column width="40%"}
<!-- Console screenshot showing bid_concept output -->
![](img/bidux_console.png){width="95%"}
:::
::::

::: {.notes}
**Package Introduction**: Generate excitement about the tooling.

- "We're not just sharing a framework - we're building tools to make it easy to adopt"
- "Our goal is to make these psychological principles accessible to every R developer"
- Emphasize this is open source - "We want this to become a community resource"
- Current features focus on documentation and knowledge
- Future features will include ready-to-use UI components with BID principles built in
- "The LLM integration will let you describe what you want in plain language"
- "Think of {bidux} as your behavioral science co-pilot for dashboard development"
- "This is in active development - we welcome contributors and collaborators"
:::

## What {bidux} Looks Like Today {background-color="#F9F9F9"}

@@

::: {.notes}
**Code Example**: Show practical usage of the package.

- "The concept dictionary gives you instant access to behavioral principles"
- "Each concept includes definition, code examples, and empirical evidence"
- "The stage documentation functions help structure your design thinking"
- "These functions integrate with dplyr workflows via pipes"
- "Documentation becomes part of your development process, not separate"
- Point out the commented future code to generate excitement
- "In Phase 2, you'll be able to generate UI templates with BID principles built in"
- When the link appears: "We're launching this at ShinyConf today - check out the repo"
:::

## SoundPulse Results {.center background-color="#4682B4"}

:::: {.columns}
::: {.column width="50%"}
### Measurable Improvements:

- Decision time reduced by 43%
- Insights per session increased by 67%
- Stakeholder satisfaction improved from 5.2/10 to 8.7/10
- Implementation time for new metrics reduced by 30%
:::

::: {.column width="50%" .fragment}
### Team Feedback:

"The BID framework transformed how we approach dashboards. What once took weeks of refinement now has clear direction from day one."

— Maya Chen, SoundPulse Research Director
:::
::::

::: {.notes}
**Results Summary**: Emphasize concrete benefits.

- "These aren't just theoretical improvements - SoundPulse measured real results"
- "43% faster decision-making means real business value"
- "67% more insights per session means better ROI on analytics investments"
- "Satisfaction scores jumped from mediocre to excellent"
- "30% faster implementation means developers saved time too"
- When the testimonial appears: "This kind of transformation is what BID is all about"
- "Maya's team went from dreading dashboard development to using it as a competitive advantage"
- "Remember, this wasn't just visual changes - this was a fundamental approach shift"
:::

@@

::: {.nonincremental}
1. **BID** helps reduce friction and improve decisions
2. **`{reactable}` + `{echarts4r}`** help bring BID to life
3. **`{bidux}`** supports you in applying BID at every stage (try it today!)
4. Build dashboards that guide — not fry — your users
:::

::: {.notes}
**Wrap-Up**: Reinforce key messages with energy.

- "BID is about reducing friction between users and insights"
- "The tools we've shown today - reactable and echarts4r - give you everything you need"
- "{bidux} is available now to help you get started - check out our GitHub"
- "Most importantly, remember this isn't just about pretty dashboards..."
- "It's about transforming how you and others make decisions with data"
- "Every dropdown you eliminate, every chart you clarify, helps someone make a better decision"
- "This is about making your users successful, not just making dashboards"
- Transition: "Thank you for your attention - we're excited to take your questions"
:::

@@

::: {.notes}
**Q&A Setup**: Prepare for questions.

- Thank the audience sincerely
- Remind them of key resources: "Remember to check out the GitHub repo at github.com/bidux"
- "We'll be around after the session if you want to chat more"
- "We'd love to hear about your dashboard challenges and how BID might help"
- For common questions, prepare brief answers:
  * "How do you measure success?" → "Start with user testing and session analytics"
  * "Does this work for technical audiences?" → "Absolutely, technical users appreciate clarity too"
  * "How long does implementation take?" → "Start small - even one principle makes a difference"
- "Don't forget to follow us on LinkedIn/GitHub for updates on {bidux} development"
:::
